In-silico molecular enrichment and clearance of the human intracranial space

### 2025-01-23 paper/main.tex
Tweak

\title{In-silico molecular enrichment and clearance of the human intracranial space}
\author[1]{Marius Causemann}
\author[1]{Miroslav Kuchta}
\author[2]{Rami Masri}
\author[1,3,*]{Marie E. Rognes }
\affil[1]{Department of Numerical Analysis and Scientific Computing, Simula Research Laboratory, Oslo, Norway}
\affil[2]{Brown University, Providence, Rhode Island, USA}
\affil[3]{K. G. Jebsen Centre for Brain Fluid Research}
\affil[*]{meg@simula.no}

@@

% What are our research questions and how do we answer them
In this study, by leveraging geometric model reduction and
mixed-dimensional modelling~\cite{masri2024modelling}, structural
magnetic resonance (MR) images~\cite{hodneland2019new}, and high
performance computing, we introduce an integrated computational model
of intracranial molecular enrichment and clearance. Focusing on the
interplay between perivascular pathways, pulsatility and CSF flow
dynamics, the model predicts the temporal evolution and spatial
distribution of a solute concentration within a detailed geometric
representation of the human SAS and ventricular system, networks of
surface PVSs and the brain parenchyma. In terms of transport dynamics,
we account for heterogeneous diffusion, dispersive mixing induced by
cardiac and respiratory pulsatility in the CSF spaces and PVSs,
convective fluid flow driven by CSF production and peristaltic
pumping, as well as solute exchange and clearance across
semi-permeable membranes. Comparing with glymphatic MRI
studies~\cite{ringstad2017glymphatic, ringstad2018brain,
  watts2019measuring}, the in-silico predictions accurately represent
molecular enrichment patterns, timing and intercompartmental
distributions. This open platform~\cite{ZENODO} thus provides a
technological opportunity for qualitatively and quantitatively
exploring key open questions relating to molecular movement within the
human brain environment such as the role of pulsatility, perivascular
pathways, structural compartmentalization, or morphological
pathologies.

>>>>

\title{In-silico molecular enrichment and clearance of the human intracranial space}
\author[1]{Marius Causemann}
\author[1]{Miroslav Kuchta}
\author[2]{Rami Masri}
\author[1,3,*]{Marie E. Rognes }
\affil[1]{Department of Numerical Analysis and Scientific Computing, Simula Research Laboratory, Oslo, Norway}
\affil[2]{Brown University, Providence, Rhode Island, USA}
\affil[3]{K. G. Jebsen Centre for Brain Fluid Research, University of Oslo, Norway}
\affil[*]{meg@simula.no}

@@

% What are our research questions and how do we answer them
In this study, by leveraging geometric model reduction and
mixed-dimensional modelling~\cite{masri2024modelling}, structural
magnetic resonance (MR) images~\cite{hodneland2019new}, and high
performance computing, we introduce an integrated computational model
of intracranial molecular enrichment and clearance. Focusing on the
interplay between perivascular pathways, pulsatility and CSF flow
dynamics, the model predicts the temporal evolution and spatial
distribution of a solute concentration within a detailed geometric
representation of the human SAS and ventricular system, networks of
surface PVSs and the brain parenchyma. In terms of transport dynamics,
we account for heterogeneous diffusion, dispersive mixing induced by
cardiac and respiratory pulsatility in the CSF spaces and PVSs,
convective fluid flow driven by CSF production and peristaltic
pumping, as well as solute exchange and clearance across
semi-permeable membranes. Comparing with glymphatic MRI
studies~\cite{ringstad2017glymphatic, ringstad2018brain,
  watts2019measuring}, the in-silico predictions accurately represent
molecular enrichment patterns, timing and intercompartmental
distributions. This open platform~\cite{ZENODO} thus provides a
technological opportunity for qualitatively and quantitatively
exploring key open questions relating to molecular movement within the
human brain environment such as the role of pulsatility, perivascular
pathways, structural compartmentalization, or morphology.
